week getbackontrack

### 2024-11-17 descriptivestry.Rmd
madepagesymlandstuff

<html lang="en">
<head>
    <meta charset="UTF-8">
    <meta name="viewport" content="width=device-width, initial-scale=1.0">
    <title>My Lab Journal</title>
    <link rel="stylesheet" href="styles.css">  <!-- Link to the CSS file I created for dark mode code chunks -->

@@

# Getting started

```{r clean}
rm(list = ls())
```

## Packages

```{r package}
require(tidyverse)
require(RSiena)
require(RsienaTwoStep)

@@

## Functions
Functions chunk 
```{r functions 1}
fpackage.check <- function(packages) {
    lapply(packages, FUN = function(x) {
        if (!require(x, character.only = TRUE)) {
            install.packages(x, dependencies = TRUE)
            library(x, character.only = TRUE)
        }
    })
}

@@

    -   descriptives (mean etc.) in whole sample

```{r sum gender}
summary(df_ego$gender)
```

    - gender counts across whole sample (0 = female, 1 = male)

```{r counts gender-all}
table(df_ego$gender)
```

    -   overall gender distribution in sample

```{r}
# Create the histogram
ggplot(df_ego, aes(x = gender))+
  geom_bar(color = "darkgrey", fill ="#B3DE69", width = 0.75)+
  labs(title = "Histogram of Gender", x = "Gender\n (0 = female, 1 = male)", y = "Count") + theme(plot.title = element_text(hjust = 0.5, face = "bold"))

@@

    -   Genders per department (0 = female, 1 = male)

```{r gender per dep.}

@@

    -   descriptives (mean etc.)
```{r summary h index}
summary(df_ego$h_index)
```
    - Overall  (INSERT YEARS STILL)

```{r hist h index}
# Histogram of prestige scores for Wave 1 
hist(df_ego$h_index, breaks = 30, main = "Distribution of H-Index from yearX to yearX",     xlab = "H Index", ylab = "Frequency", col = "#B3DE69") # INSERT YEARS OF WAVE/TIME FRAME STILL
```

    -   H index per department

```{r table per dep h index}
# Wave 1: Prestige distribution by dep. and total
df_ego %>%
    group_by(discipline.24) %>%
    summarise(mean_h_index = mean(h_index, na.rm = TRUE), min_h_index = min(h_index,
        na.rm = TRUE), max_h_index = max(h_index, na.rm = TRUE), sd_h_index = sd(h_index,
        na.rm = TRUE)) %>%
    bind_rows(df_ego %>%
        summarise(discipline.24 = "total", mean_h_index = mean(h_index, na.rm = TRUE), min_h_index = min(h_index,
            na.rm = TRUE), max_h_index = max(h_index, na.rm = TRUE), sd_h_index = sd(h_index,
            na.rm = TRUE)))
```

@@

-   Nr. of nodes

```{r nodes}
vcount(test_w1)
```

-   Nr. of edges

```{r edges}
ecount(test_w1)
```

-   Dyad census

    ```{r dyad cen}

@@

-   Triad-census

    ```{r triad cen}
igraph::triad_census(test_w1)
    ```

-   edge-density

    ```{r edge dens}
# edge density
igraph::edge_density(test_w1)
    ```

@@

-   reciprocity

    ```{r recip}
reciprocity(test_w1, ignore.loops = TRUE, mode = c("default", "ratio"))
    ```
reciprocity = 1 makes sense since the ties are undirected rn

-   degree centrality / degreee?

    ```{r degree}

@@

-   Betweenness centrality /betweenness?

    ```{r betweenness}
betweenness_w1 <- igraph::betweenness(test_w1, directed = T)
betweenness_w1 <- as.data.frame(betweenness_w1)
ggplot(betweenness_w1, aes(as.numeric(betweenness_w1), colour = as.numeric(betweenness_w1))) +
  geom_histogram(binwidth = 1.2) +
  labs(
    title = "Distribution Betweenness Wave 1",
    x = "Distribution of Betweenness",
    y = "Count")

@@

-   Clustering

    ```{r clustering}
#clustering w1
clustering_w1 <- igraph::transitivity(test_w1, type = "local")
clustering_w1 <- as.data.frame(clustering_w1)
ggplot(clustering_w1, aes(as.numeric(clustering_w1), colour = as.numeric(clustering_w1) )) +
  geom_histogram(binwidth = .05) +
  labs(
    title = "Distribution Clustering Wave 1",
    x = "Distribution of Clustering",
    y = "Count" )
    ```

@@

-   Density

    ```{r density}
density_w1 <- igraph::edge_density(test_w1)
density_w1
    ```

-   Average path length

    ```{r path length}
mean((ego_size(test_w1, order = 2, mode = "out") - 1)/vcount(test_w1))
    ```

-   Segregation

    -   Mortons I
    - also graphs below
```{r plot}

>>>>

<html lang="en">
<head>
    <meta charset="UTF-8">
    <meta name="viewport" content="width=device-width, initial-scale=1.0">
    <title>My Descriptives</title>
    <link rel="stylesheet" href="styles.css">  <!-- Link to the CSS file I created for dark mode code chunks -->

@@

# Getting started
```{r clean}
rm(list = ls())
```

## Packages
```{r package}
require(tidyverse)
require(RSiena)
require(RsienaTwoStep)

@@

## Functions

Functions chunk 
```{r functions 1}
fpackage.check <- function(packages) {
    lapply(packages, FUN = function(x) {
        if (!require(x, character.only = TRUE)) {
            install.packages(x, dependencies = TRUE)
            library(x, character.only = TRUE)
        }
    })
}

@@

descriptives (mean etc.) in whole sample
```{r sum gender}
summary(df_ego$gender)
```

gender counts across whole sample (0 = female, 1 = male)
```{r counts gender-all}
table(df_ego$gender)
```

overall gender distribution in sample
```{r}
# Create the histogram
ggplot(df_ego, aes(x = gender))+
  geom_bar(color = "darkgrey", fill ="#B3DE69", width = 0.75)+
  labs(title = "Histogram of Gender", x = "Gender\n (0 = female, 1 = male)", y = "Count") + theme(plot.title = element_text(hjust = 0.5, face = "bold"))

@@

Genders per department (0 = female, 1 = male)
```{r gender per dep.}

@@

descriptives (mean etc.)
```{r summary h index}
summary(df_ego$h_index)
```
Overall  (INSERT YEARS STILL)
```{r hist h index}
# Histogram of prestige scores for Wave 1 
hist(df_ego$h_index, breaks = 30, main = "Distribution of H-Index from yearX to yearX",     xlab = "H Index", ylab = "Frequency", col = "#B3DE69") # INSERT YEARS OF WAVE/TIME FRAME STILL
```

H index per department
```{r table per dep h index}
# Wave 1: Prestige distribution by dep. and total
df_ego %>%
    group_by(discipline.24) %>%
    summarise(mean_h_index = mean(h_index, na.rm = TRUE), min_h_index = min(h_index,
        na.rm = TRUE), max_h_index = max(h_index, na.rm = TRUE), sd_h_index = sd(h_index,
        na.rm = TRUE)) %>%
    bind_rows(df_ego %>%
        summarise(discipline.24 = "total", mean_h_index = mean(h_index, na.rm = TRUE), min_h_index = min(h_index,
            na.rm = TRUE), max_h_index = max(h_index, na.rm = TRUE), sd_h_index = sd(h_index,
            na.rm = TRUE)))
```

@@

Nr. of nodes
```{r nodes}
vcount(test_w1)
```

Nr. of edges
```{r edges}
ecount(test_w1)
```

Dyad census
    ```{r dyad cen}

@@

Triad-census
    ```{r triad cen}
igraph::triad_census(test_w1)
    ```

Edge-density
    ```{r edge dens}
# edge density
igraph::edge_density(test_w1)
    ```

@@

reciprocity
    ```{r recip}
reciprocity(test_w1, ignore.loops = TRUE, mode = c("default", "ratio"))
    ```
reciprocity = 1 makes sense since the ties are undirected rn

degree centrality / degreee?
    ```{r degree}

@@

Betweenness centrality /betweenness?
    ```{r betweenness}
betweenness_w1 <- igraph::betweenness(test_w1, directed = T)
betweenness_w1 <- as.data.frame(betweenness_w1)
ggplot(betweenness_w1, aes(as.numeric(betweenness_w1), colour = as.numeric(betweenness_w1))) +
  geom_histogram(binwidth = 1.2) +
  labs(
    title = "Distribution Betweenness Wave 1",
    x = "Distribution of Betweenness",
    y = "Count")

@@

Clustering
    ```{r clustering}
#clustering w1
clustering_w1 <- igraph::transitivity(test_w1, type = "local")
clustering_w1 <- as.data.frame(clustering_w1)
ggplot(clustering_w1, aes(as.numeric(clustering_w1), colour = as.numeric(clustering_w1) )) +
  geom_histogram(binwidth = .05) +
  labs(
    title = "Distribution Clustering Wave 1",
    x = "Distribution of Clustering",
    y = "Count" )
    ```

@@

Density
    ```{r density}
density_w1 <- igraph::edge_density(test_w1)
density_w1
    ```

Average path length
    ```{r path length}
mean((ego_size(test_w1, order = 2, mode = "out") - 1)/vcount(test_w1))
    ```

Segregation
    - Mortons I
    - also graphs below
```{r plot}

### 2024-11-17 weekbacktrack.Rmd
madepagesymlandstuff

+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------+

@@

+:==================================================================================================+:=============================================================+:================================================================+:===========================================================================================+:==============================================================================+:===============================================================================================+:=========================================================================+

@@

| ![](images/socialnetworking_meh.jpg){width="800"}Check in with Jochem                             | ![](images/used_arson%20frog.jpg){width="952"}*[university]* | ![](images/used_arson%20frog.jpg)*[university]*                 | ![](images/socialnetworking_meh.jpg)*[Depression]*                                         | ![](images/socialnetworking_meh.jpg)*[Depression]*                            | ![](images/socialnetworking.jpg){width="800"}Write data, methods, introduction, and theory [W] | ![](images/socialnetworking_meh.jpg)*[university]*                       |

@@

| Continue description & plotting [S3]                                                              |                                                              |                                                                 | Continue description & plotting [S3]                                                       | Data & methods part [W]                                                       | estimate model [S5]                                                                            | goodness of fit [S6]                                                     |

@@

|                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                                                | Start results                                                            |
+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------+

@@

| Check in with Jochem                                                                              |                                                              |                                                                 | Results [W]                                                                                | Finish Results [W]                                                            |                                                                                                | Rework intro [W]                                                         |
+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------+

>>>>

+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------------------+

@@

+:==================================================================================================+:=============================================================+:================================================================+:===========================================================================================+:==============================================================================+:===========================================================================+:=====================================================================================+

@@

| ![](images/socialnetworking_meh.jpg){width="800"}Check in with Jochem                             | ![](images/used_arson%20frog.jpg){width="952"}*[university]* | ![](images/used_arson%20frog.jpg)*[university]*                 | ![](images/socialnetworking_meh.jpg)*[Depression]*                                         | ![](images/socialnetworking_meh.jpg)*[Depression]*                            | ![](images/socialnetworking.jpg){width="800"}Write data, methods           | ![](images/socialnetworking_meh.jpg)*[university]*write introduction, and theory [W] |

@@

| Continue description & plotting [S3]                                                              |                                                              |                                                                 | Continue description & plotting [S3]                                                       | Data & methods part [W]                                                       |                                                                            | estimate model [S5]                                                                  |

@@

|                                                                                                   |                                                              |                                                                 |                                                                                            |                                                                               |                                                                            | goodness of fit [S6]                                                                 |
+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------------------+

@@

| Check in with Jochem                                                                              |                                                              |                                                                 | Results [W]                                                                                | Finish Results [W]                                                            | email Jochem if delay                                                      | Rework intro [W]                                                                     |
+---------------------------------------------------------------------------------------------------+--------------------------------------------------------------+-----------------------------------------------------------------+--------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------+----------------------------------------------------------------------------+--------------------------------------------------------------------------------------+
